Verifying Demonstrations

### 2018-05-30 paper/LocationProofs.tex

Some LBS only grant access to resources to users located at a particular location, thus raising the issue of verifying the position claimed by a particular user. 
In most of the existing schemes, the location of a user/device is determined by the device itself (\eg through GPS) and forwarded to the LBS provider. 
One of the main drawback of this approach is that a user can cheat by having his device transmitting a false location. 
Therefore, it is possible for a user to be inappropriately granted access to a particular resource while being thousands of kilometers away.

One possible way to counter this threat is by having the requesting device formally proven that it really is at the claimed location, which give rise to the concept of \emph{location proof}. 
In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. A location proof architecture is a system by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof. 
Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus 
raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
\seb{to do add the corresponding reference}
However, some location proofs systems, such as PROPS, exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location. 
\PRIVO share some similarities with PROPS, although their objective is quite different as we aim at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.

>>>>

Some location-based services only grant access to resources to users located at a particular location, thus raising the issue of verifying the position claimed by a particular user. 
In most of the existing schemes, the location of a user/device is determined by the device itself (\eg through GPS) and forwarded to the location-based service provider. 
One of the main drawback of this approach is that a user can cheat by having his device transmitting a false location. 
Therefore, it is possible for a user to be inappropriately granted access to a particular resource while being thousands of kilometers away.

One possible way to counter this threat is by having the requesting device formally proven that it really is at the claimed location, which give rise to the concept of \emph{location proof}. 
In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. A location proof architecture is a system by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof.
\seb{add references to location proof systems} 
Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
However, some location proofs systems, such as PROPS \cite{DBLP:conf/srds/GambsKRT14}, exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location. 
\PRIVO share some similarities with PROPS, although their objective is quite different as it aims at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.

### 2018-05-30 paper/RelatedWork.tex

@@

The seemingly most commonly used method for counting crowds at protests is 
\emph{Jacobs's method}, \cf~\cite{%
  2016DemonstrationsInSeoul,%
  BBCHowToCountProtestNumbers,%
  HowWillWeKnowTrumpInauguralCrowdSize,%
  TheXManMarch,%
  TheCrowdNumbersGame,%
}.
It is a manual method devised in the 1960s relying on aerial photos of the event.
The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions and finally sums them up to get an estimate of the global count.
Clearly this method is prone to errors as it is based on estimates.
It provides universal verifiability (\cref{UniversalVerif}) since anyone can redo the counting using the same photos.
However, it is difficult to achieve individual verifiability (\cref{IndividualVerif}) using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial photos.}.
We can argue that it also achieves eligibility (\cref{EligibilityVerif}) if all the photos are taken at the same point in time with no overlap, since then no one can be counted twice.
Unfortunately, we can only get the peak participation with this method.
When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the photos themselves when and where the they were taken).
However, this is prone to cheating --- and subject to a variety of 
misinformation techniques --- and the best we can do is to employ forensic 
methods to try to detect any modifications or other attempts at fraud.

From a privacy perspective, all techniques based on photo or video material are 
as privacy preserving as the protesters make themselves.
There is a risk that participants are recognizable from the material if they do 
not wear masks.

Among more recent methods, there is an application called CrowdSize~\cite{CrowdSize} that can estimate the size of a crowd 
based on a selected space.
Once the user has specified the zone, he selects one of three pre-set density estimates: light, medium or dense.
This is similar to the method usually used by police (\eg for the protests in 
Seoul):
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{p}olice presume\textins*{d} that, when sitting, six people would 
  fill a space of 
  3.3 square meters
  \textelp{}
  The same area would hold nine or 10 people when standing%
}.
This method is not verifiable unless the user takes a picture of the crowd, in which case it inherits the verifiability properties of the previous method.

In the computer vision community, there is a body of work on estimating the number of persons in a picture (\eg the work of 
\citet{NNCrowdCounting}).
This class of methods requires photos or video surveillance of the protest location during the entire protest and are thus highly privacy-invasive.
They are generally based on machine learning, and thus also require a training 
dataset to work.
In the work by \citet{NNCrowdCounting}, they actually train and evaluate their algorithm on different scenes, which might make this method easier to use for protesting.
Universal verifiability (\cref{UniversalVerif}) can be provided with this method, since someone can always recount the participants using the recorded video material.
Some degree of individual verifiability could also be provided (\cref{IndividualVerif}), if Alice can recognize her own face in the video, but this might still be difficult. 
Note also that while automatic face recognition can help verifiability, it has a high impact on privacy.
Also, it is difficult (if not impossible) to not count people twice, thus we cannot argue for eligibility (\cref{EligibilityVerif}).
In theory, this class of methods will provide an upper bound, whereas our method outputs a lower bound.
However, it is still difficult to capture the entire location on surveillance 
video, which diminishes the argument for an upper bound in practice.
The spatial and temporal verifiability properties are reduced to those of the video, which should be similar as in our discussion about the verifiability of photos (\ie, using forensic methods).

Another problem for all the above methods is exemplified by the demonstrations 
in Seoul:
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he demonstrators not only gather in open space, but also small 
  alleys and between buildings%
}.
In this situation it is very difficult to faithfully capture the situation.
Even if the photo material is taken from different angles, we will have the additional problem of not counting people twice.

During the protests in Seoul~\cite{2016DemonstrationsInSeoul}, one physical 
analytics company tried to estimate the number of participants using their 
technology.
They scanned for MAC addresses emitted from the Wi-Fi of participants' smartphones.
However, this method required many assumptions:
\blockcquote{2016DemonstrationsInSeoul}{%
  The company presumed that about half of smartphone users usually leave their Wi-Fi feature on and the other half switch it off, based on a separate survey on smartphone usage. 
It also assumed that about 20\% of the smartphone signals were repetition from the same device.
}
This method cannot provide any verifiability, as we must trust the company in doing the measurements correctly and to be honest about when and where they did them.
As MAC address randomization get wider adoption, this will be even more difficult, although some tracking of smartphones could still be possible~\cite{WhyMACRandomizationIsNotEnough}.

A better proposal would be to use \emph{IMSI catchers} (or the real cell towers of the mobile network) to count unique phones at a location.
However, there are several problems with this approach.
First, it will be difficult to register only the participants' phones, as many 
bystanders will also be counted.
It is also difficult to differentiate between the protesters and the counter-protesters.
Second, since the phone has a unique identifier, participants might be uncomfortable to be registered in association with the event and might thus turn the device off, even though, at least with 5G, the IMSI will not be
transmitted in plaintext anymore. %need to cite?
Finally, there will be limited verifiability, as the data recorder must be trusted to record all data in the relation to the protest.

In general for all of the above methods, the more a crowd spreads out, the more 
difficult it will be to determine its size.
In particular, one of the challenge is determining whether people near the event's perimeter are participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
These methods also have difficulty capturing the actual attendance of an event (\ie, the cumulative participation, not just the count at a snapshot around the peak).

One of the most closely related work to our scheme is \citet{CrowdCount}, which is a web service that lets Alice create an event such that anyone can submit his location to register that he is in Alice's event.
This method has the benefit of counting everyone who has declared his presence, not just the count at the snapshot of the photos.
However, there is no verification as the service must be trusted to behave honestly, but even then, nothing prevents Bob from submitting twice (violating eligibility, \cref{EligibilityVerif}).
Another downside is that the service also requires an Internet connection during the event to register as a participant.
This makes it prone to some form of denial-of-service attack.
For instance, if Alice has organized a protest against Grace's regime, who shuts 
down the cellular network or Internet backbone as a means to censor the protest.

Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which 
uses epidemic spreading of crowd-size estimates by device-to-device 
communication to count crowds in dense urban environments with high 
node-mobility and churn. There is, however, no consideration of a potentially 
adverserial setting and thus no verification or checks on eligibility. 
DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense 
areas, avoids double counting, but again, only work for honest participants.

>>>>

In this section, we first describe the crowd counting methods that are classically used to estimate the size of a crowd during a protest before reviewing the related work on location proof systems from which our solution \PRIVO is inspired.

@@

The seemingly most commonly used method for counting crowds at protests is \emph{Jacobs's method}~\cite{2016DemonstrationsInSeoul,BBCHowToCountProtestNumbers,HowWillWeKnowTrumpInauguralCrowdSize,TheXManMarch,TheCrowdNumbersGame}.
This manual method devised in the 1960s relies on aerial pictures of the event.
The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions before summing them up to get an estimate of the global count.
Clearly, this method is prone to errors as it is based on estimates.
It provides universal verifiability (\cref{UniversalVerif}) since anyone can redo the counting using the same pictures.
However, it is difficult to achieve individual verifiability (\cref{IndividualVerif}) using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial pictures.}.
We can argue that it also achieves eligibility (\cref{EligibilityVerif}) if all the photos are taken at the same point in time with no overlap, since then no one can be counted twice.
Unfortunately, we can only get the peak participation with this method.
When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the photos themselves when and where the they were taken).
However, this is prone to cheating --- and subject to a variety of manipulation techniques --- and the best we can do is to employ forensic methods to try to detect any modifications or other attempts of fraud.
From a privacy perspective, all techniques based on photo or video material are necessarily not privacy-preserving unless the protesters take actions to protect themselves.
For instance, there is a risk that participants are recognizable from the material if they do not wear masks.

Among more recent methods, there is an application called CrowdSize~\cite{CrowdSize} that can estimate the size of a crowd on a selected area.
Once the user has specified the zone, he selects one of three pre-set density estimates: light, medium or dense.
This is similar to the method usually used by police (\eg during the protests in Seoul):
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{p}olice presume\textins*{d} that, when sitting, six people would fill a space of 
  3.3 square meters
  \textelp{}
  The same area would hold nine or 10 people when standing%
}.
This method is not verifiable unless the user takes a picture of the crowd, in which case it inherits the verifiability properties of the previous method.

In the computer vision community, there is a body of work on estimating the number of persons in a picture (\eg the work of 
\citet{NNCrowdCounting}).
This class of methods requires pictures or video surveillance of the protest location during the entire protest and are thus highly privacy-invasive.
They are generally based on machine learning techniques, and thus also require a training dataset to work.
In the work by \cite{NNCrowdCounting}, they actually train and evaluate their algorithm on different scenes, which might make this method easier to use for protesting.
Universal verifiability (\cref{UniversalVerif}) can be provided with this method, since someone can always recount the participants using the recorded video material.
Some degree of individual verifiability could also be provided (\cref{IndividualVerif}), if Alice can recognize her own face in the video, but still this might be difficult. 
Remark also that while automatic face recognition can help verifiability, it has a high impact on privacy.
In addition, it is difficult (if not impossible) to avoid to count some people twice, thus we cannot argue for eligibility (\cref{EligibilityVerif}).
In theory, this class of methods will provide an upper bound, whereas our method outputs a lower bound.
Furthermore, it is also difficult to capture the entire location on video surveillance, which diminishes the argument for an upper bound in practice.
The spatial and temporal verifiability properties are reduced to those of the video, which should be similar as in our discussion about the verifiability of photos (\ie, using forensic methods).

Another problem for all the above methods is exemplified by the demonstrations in Seoul:
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he demonstrators not only gather in open space, but also small alleys and between buildings%
}.
In this situation it is very difficult to faithfully capture the situation.
Indeed, even if the scene is taken from different angles, there is the additional problem of not counting people twice.

During the protests in Seoul~\cite{2016DemonstrationsInSeoul}, one physical analytics company tried to estimate the number of participants using their physical analytics technology.
In a nutshell, this technology scans the MAC addresses emitted from the participants' smartphones during Wi-Fi probe requests.
However, in order to work this method makes many additional assumptions:
\blockcquote{2016DemonstrationsInSeoul}{%
The company presumed that about half of smartphone users usually leave on their Wi-Fi feature on and the other half switch it off, based on a separate survey on smartphone usage. 
It also assumed that about 20\% of the smartphone signals were repetition from the same device.
}
This method cannot provide any verifiability, as we must trust the company on performing the measurements correctly and to be honest about when and where they conducted them.
In addition, as MAC address randomization is now getting a wider adoption precisely to fight physical tracking, this method will not work any more, although some tracking of smartphones could still be possible~\cite{WhyMACRandomizationIsNotEnough}.

A better proposal would be to use \emph{IMSI catchers} (or the real cell towers of the mobile network) to count unique phones at a location.
However, there are several problems with this approach.
First, it will be difficult to register only the participants' phones, as many bystanders will also be counted.
Thus, it will not be possible to distinguish clearly between the protesters and the counter-protesters.
Second, since the phone has a unique identifier, participants might be uncomfortable to be registered in association with the event and might thus turn the device off, even though, at least with 5G, the IMSI number will not be transmitted anymore in plaintext. %need to cite?
Finally, there will be limited verifiability, as the data recorder must be trusted to record all data in relation to the protest.

In general for all of the above methods, the more a crowd spreads out, the more difficult it will be to determine its size.
In particular, one of the challenge is determining whether people near the event's perimeter are participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
These methods also have difficulty to capture the actual attendance of an event (\ie, the cumulative participation, not just the count at a snapshot around the peak).

One of the most closely related work to our scheme is \citet{CrowdCount}, which is a web service that lets Alice create an event such that anyone can submit his location to register that he is in Alice's event.
This method has the benefit of counting everyone who has declared his presence, not just the count at the snapshot of the pictures.
However, there is no verification as the service must be trusted to behave honestly, but even then, nothing prevents Bob from submitting twice (violating eligibility, \cref{EligibilityVerif}).
Another downside is that the service also requires an Internet connection during the event to register as a participant.
This makes it prone to some form of denial-of-service attack.
For instance, if Alice has organized a protest against Grace's regime, who shuts down the cellular network or Internet backbone as a means to censor the protest.

Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
However, there is no consideration of a potentially adversarial setting and thus no verification or checks on eligibility. 
Finally, DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only work withhonest participants.
\seb{mention the method used by Le Monde}

### 2018-05-30 paper/SystemModel.tex

\emph{Defining the concept of protest.} 
To be able to estimate the participation count for a protest, we first need to define this concept and which quantity should be counted.
Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul in 2016
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital city and repeated every weekend for the duration of a few weeks.
The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
We also have the Venezuelan demonstrations in 2017 in which \blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show their support for the president's controversial plan to rewrite the constitution%
}.
Generalizing from these examples, the minimal common part is the cause, \label{CauseIsTheCommonDenominator} while the location (or area) considered varies over time.

@@

\begin{definition}[Proof share]
A \emph{proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a tuple in which: \(\cid, t, l\) are as in \cref{DefProtest};
  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); and \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
  We say that \(\psh\) is part of a subprotest \(p = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by \(\psh \sqsubseteq p\).
  We define \(\pshs\) as the set of all proof shares.
\end{definition}

@@

\begin{definition}[Participation proof]%
  \label{DefParticipationProof}
  A \emph{participation proof} of protester with pseudonym \(\pid\) participating in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
  \begin{multline}
    \nonumber
    \prf_{\pid, \prtst} =
    \left\{ \psh = (\cid, t, l, \pid, \wid)\in \pshs \mid
      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\}
  \end{multline}
  of all proof shares with the same protester and protest identifiers, witnessing time interval \(t\) and location \(l\) is within those of the protest.
We denote by \(\prfs\) the set of all proofs.
\end{definition}

@@

We can now define the participation count as follows.

\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(\prtst\) (as in 
  \cref{DefParticipationProof}) as the cardinality \(|\prfs_{P}^{\str,\theta}|\) 
  of the set of participation proofs \[
    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,P} \in \prfs \mid
      \str(\prf_{i,j})\geq \theta \right\}
  \] for some strength function \(\str\colon \powerset(\pshs)\to \RR_+\) and a threshold \(\theta\).
\end{definition}

>>>>

\emph{Defining the concept of protest.} 
To be able to estimate the participation count for a protest, we first need to define this concept and which quantity should be counted.
Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul in 2016
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital city and repeated every weekend for the duration of a few weeks.
The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
We also have the Venezuelan demonstrations in 2017 in which \blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show their support for the president's controversial plan to rewrite the constitution%
}.
Generalizing from these examples, the minimal common part is the cause,%
\label{CauseIsTheCommonDenominator} while the location (or area) considered 
varies over time.

@@

\begin{definition}[Proof share]%
  \label{DefProofShare}\label{DefProofShares}
  A \emph{proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a tuple in which: 
  \(\cid, t, l\) are as in \cref{DefProtest};
  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); 
  and
  \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
  We say that \(\psh\) is part of a subprotest \(\sprtst = (\cid', t', l')\) if 
  and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
  \(\psh \sqsubseteq \sprtst\).
  We define \(\pshs\) as the set of all proof shares.
\end{definition}

@@

\begin{definition}[Participation proof]%
  \label{DefParticipationProof}\label{DefParticipationProofs}
  A \emph{participation proof} of a protester with pseudonym \(\pid\) who 
  participates in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
  \begin{multline}
    \nonumber
    \prf_{\pid, \prtst} =
    \left\{ \psh = (\cid, t, l, \pid, \wid)\in \pshs \mid
      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\}
  \end{multline}
  of all proof shares with the same protester and protest identifiers, witnessing time interval \(t\) and location \(l\) is within those of the protest.
  We denote by \(\prfs\) the set of all proofs.
\end{definition}

@@

We can now define the participation count as follows.
\begin{definition}[Participation count]%
  \label{DefParticipationCount}
  We define the \emph{participation count} of a protest \(\prtst\) (as in 
  \cref{DefParticipationProof}) as the cardinality 
  \(|\prfs_{P}^{\str,\theta}|\) of the set of participation proofs \[
    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,P} \in \prfs \mid
      \str(\prf_{i,P})\geq \theta \right\}
  \] for some strength function \(\str\colon \powerset(\pshs)\to \RR_+\) and a 
  threshold \(\theta\).
\end{definition}

### 2018-05-30 paper/ZKPK.tex
Fixes subsection error
Removes number from non-referenced eqn

\subsubsection{Zero-knowledge proofs of knowledge}%
\label{ZKPK}

We will use the notation introduced by \citet{PKnotation}:
\begin{equation}\label{PKexample}
  \PK{\alpha, \beta, \gamma}
  {y = g^\alpha h^\beta \land y' = \hat g^\gamma}
\end{equation}
which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that 
\(y, y'\) are of the form \(y = g^\alpha h^\beta\) and \(y' = \hat g^\gamma\), 
respectively.
Greek letters are known only to the prover and for which the prover wishes to 
prove knowledge, all other letters are known by the verifier.

When a proof of knowledge is turned into a signature using the Fiat-Shamir 
heuristic~\cite{FiatShamirHeuristic}, we will denote it as
\begin{equation*}\label{SPKexample}
  \sigma\gets \SPK{\alpha, \beta, \gamma}
  {y = g^\alpha h^\beta \land y' = \hat g^\gamma}
  {m},
\end{equation*}
which yields a signature \(\sigma\) on \(m\), ensuring that the issuer knew 
\(\alpha, \beta, \gamma\) such that \(y = g^\alpha h^\beta\) and \(y' = 
  \hat{g}^\gamma\).

>>>>

\subsection{Zero-knowledge proofs of knowledge}%
\label{ZKPK}

We will use the notation introduced by \citet{PKnotation}:
\begin{equation}\label{PKexample}
  \PK[\alpha, \beta, \gamma][y = g^\alpha h^\beta \land y' = \hat g^\gamma]
\end{equation}
which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that \(y, y'\) are of the form \(y = g^\alpha h^\beta\) and \(y' = \hat g^\gamma\), respectively.
Greek letters are known only to the prover and use for the information for which the prover wishes to prove knowledge, all other letters are known by the verifier.

When a proof of knowledge is turned into a signature using the Fiat-Shamir heuristic~\cite{FiatShamirHeuristic}, we will denote it as
\begin{equation*}\label{SPKexample}
  \sigma\gets \SPK[\alpha, \beta, \gamma]%
  [y = g^\alpha h^\beta \land y' = \hat g^\gamma]%
  [m],
\end{equation*}
which yields a signature \(\sigma\) on \(m\), ensuring that the issuer knows \(\alpha, \beta, \gamma\) such that \(y = g^\alpha h^\beta\) and \(y' = \hat{g}^\gamma\).
